Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-16 preamble.rnw
Fix a bug where the article/supplementary could wind up with one another's figures.

>>>>

<<include=FALSE>>=
	#Compiling more than one document in the same directory leads to theior figures overwriting one another.
	#This can lead to including the wrong figures when the TeX files are compiled into PDFs.
	#As such, we set different directories for each file's figures.
	#'jobname' must be set in the Makefile as the parent document is compiled.
	opts_chunk$set(fig.path = paste0("figures/", jobname, "/"))
@
